A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-10-21 evaluation.tex
Relabel graphs etc

The most obvious threats to validity would be poor benchmarking or poor
implementation, e.g. if the method described in \cref{sec:calculus,sec:multiple}
deviate from what is actually benchmarked in section \cref{sec:experiments}, or
if the methods used for benchmarking were unsound. To increase the probability
that our results are representative both in the sense of representing expected
inputs and, in the statistical sense, for a given run of \Catra{} despite the
use of randomness in our implementation, we execute many experiments. Moreover,
to address the issue of correctness we have validated all reported solutions
made by \Calculus{} with \Nuxmv{} to ensure that \Calculus{} is indeed sound. A
previous version contained a race condition triggered by random restarts during
product materialisation which would in about \numprint{0.7} of instances lead to
non-deterministically unsound behaviour. We have observed no instances of this
bug or any other soundness issue since fixing that bug, and in addition to
running all \NrBenchmarks{}, we have re-executed the same instances multiple
times for long durations to capture other soundness issues without any issues.

Another threat to validity would be if the competition (baseline and \Nuxmv)
would be disadvantaged in our comparison. For \Nuxmv{}, we use the default
configuration, which we believe should be performant (or it should not be the
default). Additionally, tweaking our invocation of \Nuxmv{} is explicitly made
easy for artefact reviewers. For baseline, our best argument is that the
solution we use is close to the one found in the \Ostrich{} string solver and
that it, therefore, should be realistic.

The greatest threat to validity remaining is our choice of implementation
platform and automata library. There are some signs that product computation
is inefficient, notably the good performance of low-threshold automata
materialisation that prioritises computing smaller products. This means that
\Calculus{} makes less heavy use of product computation than baseline does,
instead relying more on \Princess{}. This situation would unfairly advantage
\Calculus{} if our automata library was the bottleneck due to our automata
library being unnaturally poor. We believe this is unlikely since similar
performance issues have been reported for string solvers. Additionally,
profiling suggests that both \Princess{}-based backends spend most of their time
in \Princess{}, suggesting that the automaton implementation is not the
bottleneck. Finally, we have compared aggregate results for both native backends
when optimising the automata construction procedures and observed that the trend
in performance differences has been robust as the automata library improved
vastly.

>>>>

The most obvious threats to validity would be an unsound implementation. To
address this we have validated all reported solutions made by \Calculus{} with
\Nuxmv{}. A previous version contained a race with random restarts during
product materialisation causing non-deterministic unsoundness in \numprint{0.7}
of instances. Since addressing that bug we have observed no other soundness
issues, despite re-executing the same instances multiple times for long
durations.

The second threat to validity is our implementation of automata operations. As
\Calculus{} by design offloads some of the product computation work onto
\Princess{}, the baseline could be unfairly disadvantaged by a slow automata
product implementation. We believe this is not an issue since similar
performance issues with the baseline approach have been reported for string
solvers. Additionally, profiling shows that baseline spends most of its time in
\Princess{}, suggesting that the automaton implementation is not the bottleneck.
Finally, the difference in performance between \Calculus{} and baseline has been
robust under significant optimisation of the automata library.
